---
title: "HW5"
output: html_document
author: "Gianna Zinnen"
date: "12-01-2025"
---

Recreate the graph shown below. It shows monthly homicides in Baltimore, with a reference added for the date of the arrest of Freddie Gray and color used to show colder months (November through April) versus warmer months (May through October). There is a smooth line added to help show seasonal and long-term trends in this data.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Loading all libraries needed:
library(dplyr)
library(readr)
library(lubridate)
library(stringr)
library(tidyr)
library(tidyverse)
library(broom)
library(ggplot2)
library(ggthemes)
library(scales)
library(purrr)


```


# Setting up dataframe and proportion test:

```{r data set up, warning = FALSE}

homicides <- read_csv("data/homicide-data.csv")

homicides <- homicides %>%
  mutate(city_name = paste(city, state, sep = ", "))

head(homicides)

Baltimore <- homicides %>% 
  filter(city_name == "Baltimore, MD") %>%
  mutate(Date = ymd(reported_date))



```
